SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-28 2017-Xudong-SMT/ActaInformatica.tex
Correct some typing error and wrong notation applying.
Lx_{reach} in Th.3 should be Lx_{sat}.

Then the assignments set of $OA_1$ is $Assignments(L1, States(L1))$ and $OA_2$ is $Assignments(L2_{reach}, States(L2_{reach}))$. The computed triples are 
\[Aut_1 = \langle L1_{reach}, States(L1_{reach}), Assignments(L1, States(L1))\rangle\] and \[Aut_2 = \langle L2_{reach}, States(L2_{reach}), Assignments(L2_{reach}, States(L2_{reach}))\rangle\]

@@

Let the fixed point of $OA_1$ to be $Aut''_1$ and the fixed point of $OA_2$ to be $Aut''_2$.

For the transitions set in $Aut''_1$ and $Aut''_2$, $L1_{reach}''$ and $L2''_{reach}$, we need to check their equivalence.
At the first iteration, the unsatisfiable transitions in $OA_1$ has only one case.
\begin{align*}
&\quad Pred\and \bigwedge_i Assignments_i(L1, States(L1) \text{ is false}\\
&\quad\rightarrow Pred \and \bigwedge_j Assignments_j(L2_{reach}, States(L2_{reach})\text{ is false}\\
&\Rightarrow \forall t\in L1_{unsat} \rightarrow t\in L2_{unsat}\\
&\Rightarrow L1_{unsat}\subseteq L2_{unsat}.
\end{align*}
However, its reverse direction is not fulfilled. Recall that $L1_{reach}=L2_{reach}$, these relation can imply that,
\begin{align*}
Assignments(L1, &States(L1)\supseteq Assignments(L2_{reach}, States(L2_{reach})\\
&\supseteq Assignments(L1_{reach}-L1_{unsat}, States(L1_{reach}-L1_{unsat}))\\
&\supseteq Assignments(L2_{reach}-L2_{unsat}, States(L2_{reach}-L2_{unsat}))
\end{align*}
So after the first iteration, the unsatisfiable transitions in $OA_1$ has two cases.
\begin{align*}
&\forall t\in L1'_{unsat} \rightarrow t\in L2'_{unsat}\\
\text{ or }&\forall t\in L1'_{unsat} \rightarrow t\notin L2'_{reach}.
\end{align*}
By induction, after removing all the transitions not in the $L2''_{reach}$, we can get that $L1''_{reach}=L2''_{reach}$, subsequently, $States(L1''_{reach})=States(L2''_{reach})$,
$Assignments\\(L1''_{reach},States''_{L1_{reach}})=Assignments(L2''_{reach},States''_{L2_{reach}})$.
\end{proof}

>>>>

Then the assignments set of $OA_1$ is $Assignments(L1, States(L1))$ and $OA_2$ is $Assignments(L2_{sat}, States(L2_{sat}))$. The computed triples are 
\[Aut_1 = \langle L1_{sat}, States(L1_{sat}), Assignments(L1, States(L1))\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), Assignments(L2_{sat}, States(L2_{sat}))\rangle\]

@@

Let the fixed points $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.

For the transitions set in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
At the first iteration, the unsatisfiable transitions in $OA_1$ has only one case according to the relation between the assertions to check,
\begin{align*}
&\quad Pred\wedge \bigvee_i Assignments_i(L1, States(L1) \text{ is false}\\
&\quad\longrightarrow Pred\wedge \bigvee_j Assignments_j(L2_{sat}, States(L2_{sat})\text{ is false}\\
&\Rightarrow \forall t\in L1_{unsat} \longrightarrow t\in L2_{unsat}\\
&\Rightarrow L1_{unsat}\subseteq L2_{unsat}.
\end{align*}
However, its reverse direction is not fulfilled. Recall that $L1_{sat}=L2_{sat}$, these relations can imply that,
\begin{align*}
Assignments(L1, &States(L1))\supseteq Assignments(L2_{sat}, States(L2_{sat}))\\
&\supseteq Assignments(L1_{sat}-L1_{unsat}, States(L1_{sat}-L1_{unsat}))\\
&\supseteq Assignments(L2_{sat}-L2_{unsat}, States(L2_{sat}-L2_{unsat}))
\end{align*}
So after the first iteration, the unsatisfiable transitions in $OA_1$ has two cases,
\begin{align*}
&\forall t\in L1'_{unsat} \longrightarrow t\in L2'_{unsat}\\
\text{ or }&\forall t\in L1'_{unsat} \longrightarrow t\notin L2'_{sat}.
\end{align*}
By induction, after removing all the transitions not in the $L2''_{sat}$, we can get that $L1_{reach}=L2_{reach}$, subsequently, $States_{L1_{reach}}=States_{L2_{reach}}$,
$Assignments\\(L1_{reach},States_{L1_{reach}})=Assignments(L2_{reach},States_{L2_{reach}})$.
\end{proof}
